Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-02-18 paper/podc20ba.tex
CCS concepts (from Stefan)

@@

\appendix
\section{PPL Algorithm} \label{apx:PPL}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\begin{algorithmic}
		%        \Require 
		%        $k, \ell$,
		%        initial configuration $P_I$,
		%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
		%        \Ensure A final configuration $P_F$ 
		\STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
		\STATE{$P_0 := P_I$}
		\label{line:initcomponents}
		\FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
		\STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
		\IF{$C_1 \neq C_2$}
		\STATE {Unite the two components into a single component $C'$ and
			$\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
		\IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
			\COMMENT{i.e.~if not in the same cluster}    
		}       
		\STATE {$P_{t} = \mathit{repartition}(P_{t-1}, P_I, \mathcal{C})$} 
		\COMMENT{move to $P$ closest to $P_I$}
		\label{line:rebalance} 
		\ENDIF
		\ENDIF
		\ENDFOR
	\end{algorithmic}
	\caption{Perfect Partition Learner (\PPL)}
	\label{alg:ppl}
\end{algorithm}

\section{Ommited proofs}
\label{apx:omitted}

@@

>>>>

\ccsdesc[500]{Networks~Network algorithms}
\ccsdesc[300]{Computer systems organization~Cloud computing}
\ccsdesc[300]{Computer systems organization~Distributed architectures}

@@

\pagebreak
\appendix
\section{PPL Algorithm} \label{apx:PPL}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\begin{algorithmic}
		%        \Require 
		%        $k, \ell$,
		%        initial configuration $P_I$,
		%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
		%        \Ensure A final configuration $P_F$ 
		\STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
		\STATE{$P_0 := P_I$}
		\label{line:initcomponents}
		\FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
		\STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
		\IF{$C_1 \neq C_2$}
		\STATE {Unite the two components into a single component $C'$ and
			$\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
		\IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
			\COMMENT{i.e.~if not in the same cluster}    
		}       
		\STATE {$P_{t} = \mathit{repartition}(P_{t-1}, P_I, \mathcal{C})$} 
		\COMMENT{move to $P$ closest to $P_I$}
		\label{line:rebalance} 
		\ENDIF
		\ENDIF
		\ENDFOR
	\end{algorithmic}
	\caption{Perfect Partition Learner (\PPL)}
	\label{alg:ppl}
\end{algorithm}

\section{Omitted proofs}
\label{apx:omitted}

@@

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10003033.10003068</concept_id>
	<concept_desc>Networks~Network algorithms</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10010520.10010521.10010537.10003100</concept_id>
	<concept_desc>Computer systems organization~Cloud computing</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10010520.10010521.10010537</concept_id>
	<concept_desc>Computer systems organization~Distributed architectures</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}
